Adolescent well-being in the digital age

### 2022-01-27 00-clean.qmd
Fix GWP internet summary table

gwp %>%
  select(region, country, year, gwpi) %>%
  mutate(internet = internet * 100) %>%
  mutate(region = str_replace(region, "_", " ")) %>%
  pivot_wider(names_from = year, values_from = internet) %>%
  select(-country) %>%
  tbl_summary(
    by = region,
    missing = "no",
    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
  ) %>%
  add_overall(col_label = "Total") %>%
  as_kable_extra(caption = "ITU summary") %>%
  row_spec(0, bold = TRUE) %>%
  kable_custom()
```

>>>>

gwp %>%
  filter(year >= 2015) %>% 
  group_by(region, country, year) %>%
  summarise(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(gwpi = gwpi * 100) %>%
  mutate(region = str_replace(region, "_", " ")) %>%
  arrange(year, region, country) %>% 
  pivot_wider(names_from = year, values_from = gwpi) %>%
  select(-country) %>%
  tbl_summary(
    by = region,
    missing = "no",
    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
  ) %>%
  add_overall(col_label = "Total") %>%
  as_kable_extra(
    caption = "GWP Internet use summary (mean over demographics)"
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_custom()
```
